This section contains descriptions of the tests.

\paragraph{ReqNo1-T}\mbox{}\\ % Lasse
Requirement: \textit{The system shall comprise at least three modes, manual, semi-automatic and automatic.}\\
The ability for the pilot to select each mode is tested. The operator will select each mode(manual, semi-automatic, automatic), using available inputs to the mission computer to confirm that these modes exist.

\subparagraph{Inputs:}
	\begin{itemize}
	\item Manual mode.
	\item Semi-automatic mode.
	\item Automatic mode.
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item Confirmation of manual mode from the system to the mission computer.
	\item Confirmation of semi-automatic mode from the system to the mission computer.
	\item Confirmation of automatic mode from the system to the mission computer.
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item Entering each mode is confirmed by the mission computer.
	\end{itemize}

\paragraph{ReqNo2-T}\mbox{}\\ % Lars N
Requirement: \textit{Manual mode shall dispense the program selected by the pilot. The pilot may select payload, and dispense direction as defined by UR-2.}
\\
The operator will dispense the desired payload in the desired direction. All combinations of payload and direction is tested.
\\
	\subparagraph{Inputs:}
	\begin{itemize}
	\item Desired dispensing combination.
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item Chaffs or flares.
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item The dispensed payload is either chaff or flare corresponding to the one selected. The payloads are dispensed in every selected direction.
	\end{itemize}

\paragraph{ReqNo3-T}\mbox{}\\ % Sergiu
Requirement: \textit{Semi automatic shall initiate an intelligent threat response upon consent from the pilot.}
\\
This test verifies that the cockpit unit, in semi automatic mode, can send a signal that requests the pilots consent before deploying the payload. All combinations of payload and direction is tested
\\
	\subparagraph{Inputs:}
	\begin{itemize}
	\item Pilots consent.
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item Chaffs or flares.
	\item None.
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item The dispensed payload is either chaff or flare corresponding to the one selected. The payloads are dispensed in every selected direction.
	\item Nothing is dispensed because the pilot did not give his consent.
	\end{itemize}


\paragraph{ReqNo4-T}\mbox{}\\ % Lars J
Requirement: \textit{Automatic mode shall initiate an intelligent threat response without pilot interaction.}\\
A threat is simulated and the cockpit unit sends a signal to the dispenser. The dispenser then dispenses the payload.
\\
	\subparagraph{Inputs:}
	\begin{itemize}
	\item Simulated threat
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item Chaffs or flares.
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item The cockpit unit sends a signal to the dispenser. The dispenser then dispenses the payload.
	\end{itemize}



\paragraph{ReqNo5-T}\mbox{}\\ % Ivan
Requirement: \textit{The pod shall include a minimum of eight standard magazines.}\\

The test official verifies that the pod includes a minimum of eight standard magazines.

\subparagraph{Expected result:}
	\begin{itemize}
	\item The pod includes a minimum of eight standard magazines.
	\end{itemize}

\paragraph{ReqNo6-T}\mbox{}\\ % Fatemeh
Requirement: \textit{The pod shall be able to dispense forwards, downwards and sideways.}\\
This test verifies the mechanical capability and reliability. The test applies to the pod components, meaning magazines and dispensers.
	\subparagraph{Inputs:}
	\begin{itemize}
	\item Dispensing commands for forward, downward and sideways directions
	\item The complete pod unit
	\item timer
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item Status output of the dispenser
	\item Direction of movement after the command applied
	\item Time taken from the dispense command to actual dispense
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item The movement directions of pod be in accordance with the dispenser commands and be applied in a fraction of second.
	\end{itemize}
\paragraph{ReqNo7-T}\mbox{}\\ % Lasse
Requirement: \textit{The cockpit unit shall be able to power ON and OFF the dispensing system and the MWS.}
\\
The test official turns on the dispenser assembly and the MWS using the mission computer. It is verified that the dispensing assembly and the MWS is on. Similarly turning off the MWS and dispenser assembly is also verified.

\subparagraph{Inputs:}
	\begin{itemize}
	\item Switch on
	\item Switch off
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item The MWS and dispenser assembly turns on.
	\item The MWS and dispenser assembly turns off.
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item The MWS and dispenser assembly can be turned on and off.
	\end{itemize}


\paragraph{ReqNo8-T}\mbox{}\\ % Lars N
Requirement: \textit{The system shall be able to dispense a minimum of two payloads within 0.1 sec.}
\\
Using manual mode, the operator tries to dispense two payloads simultaneously. It is measured whether the payloads are dispensed within 0.1 sec.
\\
	\subparagraph{Inputs:}
	\begin{itemize}
	\item Manual mode
	\item Dispensing command
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item Confirmation of manual mode from the system to the mission computer.
	\item Two payloads.
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item The two payloads are dispensed within 0.1 sec.
	\end{itemize}

\paragraph{ReqNo9-T}\mbox{}\\ % Sergiu
Requirement: \textit{The system shall be able to dispense a pattern of payloads programmable by the customer.}
\\
This test verifies that the program outputs in the desired pattern that was programmed by the customer. Afterwards it is loaded and tested on the pod to see the it dispense in the desired pattern.
\\
	\subparagraph{Inputs:}
	\begin{itemize}
	\item Manual mode
	\item Dispensing command
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item Confirmation of manual mode from the system to the mission computer.
	\item Chaffs or flares.
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item The payloads are dispensed as programmed by the customer
	\end{itemize}


\paragraph{ReqNo11-T}\mbox{}\\ % Lars J
Requirement: \textit{The System shall be able to erase prior defense patterns and usage statistics upon receiving the string 'zeroize' from the mission computer.}\\
	\subparagraph{Inputs:}
	\begin{itemize}
	\item 'zeroize' string
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item Confirmation of erasure.
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item The system has erased prior defense patterns and usage statistics.
	\end{itemize}

\paragraph{ReqNo12-T}\mbox{}\\ % Ivan
Requirement: \textit{The cockpit unit shall communicate with the MWS via a MIL-STD-1553-B data bus.}\\
The test official verifies that the communication bus between the cockpit unit and the MWS is a MIL-STD-1553-B data bus.

\subparagraph{Expected result:}
	\begin{itemize}
	\item The communication bus between the cockpit unit and the MWS is a MIL-STD-1553-B data bus.
	\end{itemize}

\paragraph{ReqNo13-T}\mbox{}\\ % Fatemeh
Requirement: \textit{Threats shall be transmitted to the aircraft mission computer in body frame format (relative to aircraft) for displaying purposes.}\\
The test includes simulating different types of threats from different directions and testing the reliability of the aircraft mission computer for displaying the threat.
	\subparagraph{Inputs:}
	\begin{itemize}
	\item Threats
	\item Timer
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item Mission computer
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item The display shows illustratively the coming threats for different directions.
	\end{itemize}
\paragraph{ReqNo14-T}\mbox{}\\ % Lasse
Requirement: \textit{Threat information will be provided by the Electronics Control Unit (ECU).}\\
A threat i simulated. By monitoring the interface I-IF-MWSCTRL(defined in section 6 of F-DDD-2014-V), it is then verified, that threat information is provided.

	\subparagraph{Inputs:}
	\begin{itemize}
	\item A simulated threat. 
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item Threat information
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item The threat information is provided by the ECU.
	\end{itemize}
	

\paragraph{ReqNo15-T}\mbox{}\\ % Lars N
Requirement: \textit{The system shall provide the aircraft mission computer
with status information and built-in test results.}
\\
Test-software installed on the mission computer requests status information and built-in test results from the system. The test-software verifies that the received data is correct.
\\
	\subparagraph{Inputs:}
	\begin{itemize}
	\item Command that requests status information and built-in test results. 
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item Status information
	\item Built-in test results
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item The status information and built-in test results is provided by the system.
	\end{itemize}

\paragraph{ReqNo16-T}\mbox{}\\ % Sergiu
Requirement: \textit{The system shall interface the aircraft intercom system to provide audio cues and warnings.}
\\
This test verifies that the aircraft intercom system receives information from the system.
\\
	\subparagraph{Inputs:}
	\begin{itemize}
	\item Relevant information that needs to trigger audio cues and warnings.
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item Audio cues
	\item Audio warnings
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item The audio information work as programmed and can provide valuable
	feedback for the pilot during the mission.
	\end{itemize}


\paragraph{ReqNo17-T}\mbox{}\\ % Lars J
Requirement: \textit{The system status on individual LRU level shall be provided by cockpit unit.}\\

\subparagraph{Inputs:}
	\begin{itemize}
	\item Status request for all Pod components.
	\end{itemize}
\subparagraph{Outputs:}
	\begin{itemize}
	\item Status information from all Pod components to the cockpit unit.
	\end{itemize}
\subparagraph{Expected result:}
	\begin{itemize}
	\item All status information is sent from the cockpit unit.
	\end{itemize}


\paragraph{ReqNo18-T}\mbox{}\\ % Ivan
Requirement: \textit{The MWS must receive navigation data from the aircraft mission computer with a latency of no more than
10 ms. Navigation data includes aircraft attitude,heading, altitude and GPS data.}\\

Navigation data is sent from the aircraft mission computer to the MWS. The time elapsed from the start of transmission to the end of reception is measured.
\subparagraph{Inputs:}
	\begin{itemize}
	\item Navigation data from aircraft mission computer
	\item Start transmission time stamp
	\end{itemize}
\subparagraph{Outputs:}
	\begin{itemize}
	\item Navigation data in the MWS
	\item End reception time stamp
	\end{itemize}
\subparagraph{Expected result:}
	\begin{itemize}
	\item The navigation data is received by the MWS.
	\item The time difference between the start and end timestamps is less than 10 ms. 
	\end{itemize}

\paragraph{ReqNo20-T}\mbox{}\\ % Fatemeh
Requirement: \textit{The cockpit unit shall communicate with the mission computer via a MIL-STD-1553-B data bus.}\\
Test includes sending commands to the mission computer and making it understandable for the pilot.
	\subparagraph{Inputs:}
	\begin{itemize}
	\item Cockpit unit
	\item MIL-STD-1553-B data bus
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item Mission computer
	\item pilot
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item The communication from the cockpit unit and the computer mission be flawless and understandable by a pilot.
	\end{itemize}
	
\paragraph{ReqNo21-T}\mbox{}\\ % Lasse
Requirement: \textit{Introduction of the system may not compromise the operation of the current weapon systems.}
\\
Every current weapon system is tested. The test of each weapon system is carried out as described by the test description of that system.

	\subparagraph{Inputs:}
	\begin{itemize}
	\item Appropriate test input for each weapon system.
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item Appropriate output of a successful test for each weapon system.
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item All weapons systems operate as before the self-protection suite was installed.
	\end{itemize}

\paragraph{ReqNo22-T}\mbox{}\\ % Lars N
Requirement: \textit{The system shall include a hardware implemented safety interlock to prevent dispensing on ground.}
\\
It is assured that the aircraft is touching the ground. Then it is tried to dispense payloads. It is observed whether the system dispenses the payload or not.
\\
	\subparagraph{Inputs:}
	\begin{itemize}
	\item Command that makes the system dispense payloads 
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item A warning signal from the cockpit unit interface.
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item The system will not dispense on ground. Instead a warning signal will be provided from the cockpit unit.
	\end{itemize}

\paragraph{ReqNo23-T}\mbox{}\\ % Sergio
Requirement: \textit{The hardware implemented safety lock shall be activated when the landing gear is on the ground.}
\\
This test verifies that the safety lock activates and remains active while the
landing gear is on the ground.
\\
	\subparagraph{Inputs:}
	\begin{itemize}
	\item Landing gear on the ground.
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item Safety lock active.
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item The sfatey lock is active.
	\end{itemize}


\paragraph{ReqNo24-T}\mbox{}\\ % Lars J
Requirement: \textit{The system shall be able to erase sensitive data upon input from a discrete zeroize signal from aircraft.}\\
	\subparagraph{Inputs:}
	\begin{itemize}
	\item 'zeroize' string
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item Confirmation of erasure.
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item The cockpit unit recieves 'zeroize' string and initiates the erasing of prior defense patterns and usage statistics.
	\end{itemize}


\paragraph{ReqNo25-T}\mbox{}\\ % Ivan
Requirement: \textit{The zeroize signal shall be received by the cockpit unit.}\\

The zeroize signal is transmitted to the cockpit unit. 
\subparagraph{Inputs:}
	\begin{itemize}
	\item Zeorize signal transmission
	\end{itemize}
\subparagraph{Outputs:}
	\begin{itemize}
	\item Zeorize signal reception by the cockpit unit
	\end{itemize}
\subparagraph{Expected result:}
	\begin{itemize}
	\item The cockpit unit receives the zeroize signal 
	\end{itemize}

\paragraph{ReqNo26-T}\mbox{}\\ % Fatemeh
Requirement: \textit{The magasines shall be stored at no lower than -10 degrees Celcius and no higher than 70 degrees Celcius.}
The temperature at which the magasines are stored shall be verified to be between -10 degrees Celcius and 70 degrees Celcius.
	\subparagraph{Inputs:}
	\begin{itemize}
	\item Storage rooms for magazines with accurate temperature control 
	\item magazines
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item Measured temperature
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item The temperature of the storage room for the magazines does not go out of -10 to 70 degree Celcius. 
	\end{itemize}
\paragraph{ReqNo27-T}\mbox{}\\ % Lasse
Requirement: \textit{The pod structure must be functional when exposed to steady state acceleration levels of 4g forward, 2.5g backward, 22g upward or 10g downward.}
\\
Each acceleration level and direction specified in requirement no. 27 of F-SRS-2014-V1 is applied the pod structure. The pod structure is then inspected for damages that may reduce functionality.

	\subparagraph{Inputs:}
	\begin{itemize}
	\item Acceleration levels and directions specified in requirement no. 27 of F-SRS-2014-V1.
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item None.
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item The pod has no damages that may reduce functionality.
	\end{itemize}


\paragraph{ReqNo28-T}\mbox{}\\ % Lars N
Requirement: \textit{The total weight of pod cannot exceed 270 kg.}
\\
The total weight of pod measured is measured using a weighing scale. It is noted whether the weight is above or below 270 kg.
\\
	\subparagraph{Inputs:}
	\begin{itemize}
	\item None.
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item Weight.
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item The weight of the pod is below 270 kg.
	\end{itemize}

\paragraph{ReqNo29-T}\mbox{}\\ % Sergiu
Requirement: \textit{The pod shall be operational at temperatures of maximum 134 degree celsius on outer skin and 152 degree celsius on leading edge for maximum 3 minutes.}
\\
This test verifies that the pod is operational at temperatures of up to 134 celsius on the outer skin. It also checks that the pod is operational after it was subjugated to a temperature of 152 degrees for 3 minutes.
\\

	\subparagraph{Expected result:}
	\begin{itemize}
	\item The pod is still operational after it has been submited to the different
	enviormental factors mentioned above.
	\end{itemize}



\paragraph{ReqNo41-T}\mbox{}\\ % Lars J
Requirement: \textit{The pod shall be operational at temperatures of maximum 95 degrees Celcius on outer skin and 152 degrees Celcius on leading egde for a maximum of 25 minutes.}\\

The pod is heated to 95 degrees Celcius on outer skin and 152 degrees Celcius on leading egde for 25 min. 

	\subparagraph{Expected result:}
	\begin{itemize}
	\item The pod is still operational.
	\end{itemize}

\paragraph{ReqNo30-T}\mbox{}\\ % Ivan
Requirement: \textit{The system shall include a hardware implemented safety interlock to prevent dispensing on ground.}\\

The test official verifies that the system includes a hardware implemented safety interlock. \\
The test official attempts to dispense the payload.  
\subparagraph{Inputs:}
	\begin{itemize}
	\item Hardware implemented safety interlock
	\item Dispense payload signal
	\end{itemize}
\subparagraph{Outputs:}
	\begin{itemize}
	\item No outputs
	\end{itemize}
\subparagraph{Expected result:}
	\begin{itemize}
	\item The system includes a hardware implemented safety interlock.
	\item When the payload dispensing is attempted, nothing happens since the hardware implemented safety interlock prevents dispensing on ground.
	\end{itemize}

\paragraph{ReqNo31-T}\mbox{}\\ % Fatemeh
Requirement: \textit{The system shall provide a method of loading software to MWS.}\\
The system applied the method for loading software.
	\subparagraph{Inputs:}
	\begin{itemize}
	\item Software for MSW
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item Method for applying the software
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item Working method for applying the SW software.
	\end{itemize}
\paragraph{ReqNo35-T}\mbox{}\\ % Lasse
Requirement: \textit{The physical dimensions of the pod cannot exceed 0.5$\times$0.5$\times$5 meter.}
\\
The dimensions of the pod is measured using a measuring tape.

	\subparagraph{Inputs:}
	\begin{itemize}
	\item None.
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item Dimensions.
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item The dimensions of the pod does not exceed 0.5$\times$0.5$\times$5 meter.
	\end{itemize}


\paragraph{ReqNo36-T}\mbox{}\\ % Lars N
Requirement: \textit{The aircraft has to be loaded with the payloads before take-off.}
\\
The aircraft is loaded with payloads before take-off. In air it is attempted to dispense the payloads. It is checked whether the loaded payloads are dispensed.
\\
	\subparagraph{Inputs:}
	\begin{itemize}
	\item Payloads
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item Payloads
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item The aircraft is able to dispense the payloads that are loaded on the aircraft.
	\end{itemize}


\paragraph{ReqNo37-T}\mbox{}\\ % Sergiu
Requirement: \textit{Pilots must be educated in handling the system from the cockpit.}
\\
This test verifies that the pilots are properly trained in handling the system from the cockpit.
\\
\subparagraph{Expected result:}
	\begin{itemize}
	\item The pilots have attended and passed the training course provided by Terma	A/S.
	\end{itemize}

\paragraph{ReqNo38-T}\mbox{}\\ % Lars J
Requirement: \textit{Technicians must be educated in maintenance of the system.}\\

\subparagraph{Expected result:}
	\begin{itemize}
	\item The technicians have attended and passed the maintenance course provided by Terma A/S.
	\end{itemize}

\paragraph{ReqNo39-T}\mbox{}\\ % Ivan
Requirement: \textit{The chaffs and flares shall be transported in accordance to Military Standard Transportation and Movement Procedures (MILSTAMP).}\\

The test official verifies that the chaffs and flares are transported in accordance to Military Standard Transportation and Movement Procedures (MILSTAMP).

\subparagraph{Expected result:}
	\begin{itemize}
	\item The chaffs and flares are transported in accordance to Military Standard Transportation and Movement Procedures (MILSTAMP).
	\end{itemize}

\paragraph{ReqNo40-T}\mbox{}\\ % Fatemeh
Requirement: \textit{The chaffs and flares shall be labeled and packed in accordance to MIL-STD-2073-1E}\\
Packing and labelling of chaffs and flares must comply with MIL-STD-2073-1E.
	\subparagraph{Inputs:}
	\begin{itemize}
	\item Packing and labelling mechanism
	\item Chaffs and flares
	\item MIL-STD-2073-1E standard
	\end{itemize}
	\subparagraph{Outputs:}
	\begin{itemize}
	\item Status of standard follow-up
	\end{itemize}
	\subparagraph{Expected result:}
	\begin{itemize}
	\item The packing and labelling of chaffs and flares complies with MIL-STD-2073-1E.
	\end{itemize}